\subsection{UCDP conflict data}

I use observations from the UCDP Georeferenced Event Dataset (GED, data version 24.1, final-coded events; codebook: \citealt{ucdp_codebook}), using best-estimate fatality counts from 2020--2024 aggregated to the PRIO-GRID cell-month level (a $0.5^\circ \times 0.5^\circ$ geographic grid cell observed in a single calendar month, the standard spatiotemporal unit in VIEWS-format evaluations). I pool state-based, non-state, and one-sided violence and retain cell-months with at least one recorded fatality; historical uncertainty is derived from cells with $\geq 3$ active months during 1989--2019. This yields 19{,}397 cell-months from 2{,}065 cells. This sample covers the active-conflict portion of the evaluation space; the roughly 800{,}000 cell-months with zero recorded fatalities are excluded because $F_\text{obs}$ degenerates to a step function at zero and the reformulation reduces to classical CRPS. The results therefore characterise the regime where observational uncertainty is operative, not the full VIEWS evaluation grid.

\subsection{Synthetic forecast versions}

The controlled and empirical comparisons use two synthetic forecast versions, both centred on the reported best estimate $y$, isolating the spread dimension:
\begin{itemize}
    \item \textbf{Tight (overconfident):} $\text{LogNormal}(\log y, \, 0.05)$---concentrates nearly all probability mass on a single value, claiming to know the truth precisely. This is the version classical CRPS is expected to prefer: its narrow CDF minimises the squared distance to the step indicator at $y$.
    \item \textbf{Honest:} A wider distribution matching the observational uncertainty. In the controlled demonstration, $\text{LogNormal}(\log y, \, \sigma_\text{honest})$ with $\sigma_\text{honest} = 0.4$ (matching the Constructor~3 default). In the empirical comparison, $\text{LogNormal}(\log y, \, \hat{\sigma}_\text{cell})$, where $\hat{\sigma}_\text{cell} = \sqrt{\log(1 + \text{CV}^2)}$ is derived from each cell's historical coefficient of variation. Median $\hat{\sigma}_\text{cell} = 0.97$; interquartile range $[0.81, 1.16]$; clipped to $[0.1, 2.0]$ (affecting 1.1\% of cell-months).
\end{itemize}
Both versions share the same location; the only difference is spread. Centering on the reported value $y$ is information unavailable at prediction time---this is a deliberate design choice that isolates whether the metric values uncertainty quantification, not whether it changes selection between genuinely different systems. The HydraNet validation (\S6.3) tests whether the reversal survives genuine location error.

\subsection{HydraNet: an operational forecaster}

HydraNet \citep{VonDerMaase2025hydranet} is a deep neural network for conflict forecasting that uses Monte Carlo Dropout \citep{gal2016dropout} for uncertainty quantification. The model is trained on VIEWS data at PRIO-GRID resolution and produces 64 MC Dropout predictive samples per cell-month\footnote{The HydraNet architecture draws 128 samples per cell-month in its reference configuration; the validation here uses 64 due to local memory constraints.} for each violence type. I test all three violence types to parallel the per-type structure of the synthetic comparison (Table~\ref{tab:per_type}).

The model is trained on January 1990--December 2016 and produces 36-step-ahead calibration predictions for January 2017--December 2020, using 13 rolling-origin sequences.\footnote{The calibration partition overlaps with training data, making this a weaker out-of-sample test than a held-out validation partition. The reversal pattern is nonetheless informative: it tests whether the reformulation changes rankings between the same model's full and stripped uncertainty, not whether the model generalises well.} I match these against UCDP fatality actuals for each violence type, using the shortest-horizon prediction available for each cell-month. Table~\ref{tab:hydranet_sample} reports the sample sizes. For each cell-month, I construct two versions of the same model's output:
\begin{itemize}
    \item \textbf{Full MC Dropout:} the model's 64 predictive samples, used directly as the forecast distribution.
    \item \textbf{Tight:} $\text{LogNormal}(\log \bar{x}, \, 0.05)$ where $\bar{x}$ is the predictive mean---a version that retains the model's location estimate but discards its uncertainty quantification.
\end{itemize}
Both versions share the same location; the only difference is spread.

\begin{table}[h]
    \centering
    \small
    \begin{tabular}{lrrr}
        \toprule
        Violence type & Cell-months & Unique cells & Factor-of-two \\
        \midrule
        State-based & 5{,}372 & 937 & 589 (11.0\%) \\
        Non-state & 2{,}130 & 549 & 188 (8.8\%) \\
        One-sided & 2{,}702 & 816 & 148 (5.5\%) \\
        \bottomrule
    \end{tabular}
    \caption{HydraNet calibration sample sizes by violence type. ``Cell-months'' counts cell-months where the reported best estimate is positive. ``Factor-of-two'' counts cell-months where the model's predictive mean falls within a factor of two of the reported value---the regime where predictive-location error is moderate and the spread dimension becomes consequential.}
    \label{tab:hydranet_sample}
\end{table}
